pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-20 article.tex
Reword model definitions

The goal of \verb;pirouette; is to measure the inference error BEAST2
makes from a given reconstructed phylogeny. For this measurement,
two models need to be specified. Both models are defined as a combination of 
site model, clock model and a tree prior. The two kind of models are a 
generative and inference model. The generative model is used to simulate 
alignments, the inference model is used to produce a posterior. 
Generative models always use a (constant-rate) birth-death tree prior.

>>>>

The goal of \verb;pirouette; is to measure the inference error BEAST2
makes from a given reconstructed phylogeny. For this measurement,
two models need to be specified: a generative and an inference model.
A generative model is a combination of site model, clock model and tree prior,
used to simulate alignments. An inference model is a combination of 
site model, clock model, tree prior, an optional node calibration prior
and setup of the Markov chain Monte Carlo (MCMC) algorithm, 
used to produce a posterior. Node calibration priors, called 'most
recent common ancestor' (MRCA) priors within BEAST2 allow, among others,
to specify a crown age.
